### 2022-09-22 sections/bdt_Htautau.tex
uopdate referee's comments

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (`Pre-Fit') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: (a) $t_{\ell}\thadhad$,
 (b) $t_{\ell}\tauhad$-1j,  (c) $t_{\ell}\tauhad$-2j, (d) $t_h\tlhad$-2j, (e) $t_h\tlhad$-3j, (f) $t_{\ell}\thadhad$-SS, (g) $t_h\thadhad$-2j, (h) $t_h\thadhad$-3j and (i) $t_h\thadhad$-3j SS.
 The total statistical and systematic uncertainty of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. `Other MC' (`Rare') includes single-top, $V$+jets, and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled by a
 normalisation factor of either 2, 10, or 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratio of data to prediction.}
\label{fig:taupt_prefit}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Distributions of the visible invariant mass of the di-$\tau$ system ($m_{\tau\tau}$) obtained before the fit to data (`Pre-Fit') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: (a) $t_{\ell}\thadhad$,
 (b) $t_{\ell}\tauhad$-1j,  (c) $t_{\ell}\tauhad$-2j, (d) $t_h\tlhad$-2j, (e) $t_h\tlhad$-3j, (f) $t_{\ell}\thadhad$-SS, (g) $t_h\thadhad$-2j, (h) $t_h\thadhad$-3j and (i) $t_h\thadhad$-3j SS.
 The total statistical and systematic uncertainty of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. `Other MC' (`Rare') includes single-top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled by a normalisation factor of either 2, 10, or 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratio of data to prediction.}
\label{fig:mtt}
\end{figure}

>>>>

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b3j_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhan 3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b3jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b3jss_log_.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (`Pre-Fit') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: (a) $t_{\ell}\thadhad$,
 (b) $t_{\ell}\tauhad$-1j,  (c) $t_{\ell}\tauhad$-2j, (d) $t_h\tlhad$-2j, (e) $t_h\tlhad$-3j, (f) $t_{\ell}\thadhad$-SS, (g) $t_h\thadhad$-2j, (h) $t_h\thadhad$-3j and (i) $t_h\thadhad$-3j SS.
 The total statistical and systematic uncertainty of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. `Other MC' includes single-top, $V$+jets, and other small backgrounds in the leptonic and hadronic channel. The $tuH$ signal is scaled by a
 normalisation factor of either 2, 10, or 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratio of data to prediction. Arrows in the figures indicate zero entries in the bins.}
\label{fig:taupt_prefit}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Distributions of the visible invariant mass of the di-$\tau$ system ($m_{\tau\tau}$) obtained before the fit to data (`Pre-Fit') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: (a) $t_{\ell}\thadhad$,
 (b) $t_{\ell}\tauhad$-1j,  (c) $t_{\ell}\tauhad$-2j, (d) $t_h\tlhad$-2j, (e) $t_h\tlhad$-3j, (f) $t_{\ell}\thadhad$-SS, (g) $t_h\thadhad$-2j, (h) $t_h\thadhad$-3j and (i) $t_h\thadhad$-3j SS.
 The total statistical and systematic uncertainty of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. `Other MC' includes single-top, and $V$+jets and other small backgrounds in the leptonic and hadronic channels. The $tuH$ signal is scaled by a normalisation factor of either 2, 10, or 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratio of data to prediction.}
\label{fig:mtt}
\end{figure}
